Dependently Typed Languages in Statix

### 2022-10-27 paper-evcs/paper.tex
Add Jespers text

@@

>>>>

\DeclareUnicodeCharacter{03BB}{L}
\DeclareUnicodeCharacter{03A0}{M}

@@

There exist several so-called \emph{logical frameworks}, tools designed specifically for implementing and experimenting with dependent type theories, such as ALF~\cite{MagnussonN93}, Twelf~\cite{PfenningS99}, Dedukti~\cite{BoespflugCH12}, Elf~\cite{pfenning_1991} and Andromeda~\cite{BauerHP20}. Since these tools are designed specifically for the task, implementing the type system takes less effort in them compared to Spoofax, but for other tasks such as defining a parser or editor services they are not as well equipped. Some logical frameworks such as Twelf and Dedukti support Miller's \emph{higher-order pattern unification}~\cite{Miller89}, which can be used as a more powerful way of inferring implicit arguments than the first-order unification built into Statix. Andromeda 2 also supports \emph{extensionality rules} that can match on the type of an equality. We expect that adding extensionality rules to our implementation would be possible to do in Statix, but we leave an actual implementation to future work.
